A Minimal Demo of \texttt{glyphmaps}

### 2012-06-01 paper/demo.Rnw
Changed merge overlaps method. Added seasonal data from glyph-maps paper.

\title{A Minimal Demo of ggplyr/glyphmaps/modelglyphs}

@@

\maketitle
This document demonstrates the basic features of the \texttt{ggplyr} package (name may change). \texttt{ggplyr} was written to create plots like the ones below. Each plot was made with \texttt{ggplyr}. The first two plots recreate plots from \citet{wickham2011split}. The last two recreate plots from \citet{wickham2012glyph}.

<<plyr star glyphs>>=
@

<<plyr filled star glyphs>>=
@

<<glyph maps grided>>=
@

>>>>

\title{A Minimal Demo of \texttt{glyphmaps}}

@@

\maketitle
This document demonstrates the basic features of the \texttt{glyphmaps} package (name may change). \texttt{glyphmaps} was written to create plots like the ones below. Each plot is made with \texttt{glyphmaps}. They recreate Figures 8 and 10a from \citet{wickham2012glyph}. To run the examples in this document please download the \texttt{glyphmaps} package with the code below.

<<install>>=
library(devtools)
install_github("ggplyr", "garrettgman", "glyphmaps")
library(glyphmaps)
@

<<glyphmaps-fig-8>>=
p <- ggplot(seasons) + 
  map_us +
  glyph(
    geom_line(aes(x = time, y = pred)), 
    major = aes(lon[1], lat[1]), glyph.by = "stn", 
    ref = ref_box(aes(fill = avg)))
@
